%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Generic template for TFC/TFM/TFG/Tesis
%
% $Id: versiones.tex,v 1.6 2020/03/24 17:18:13 macias Exp $
%
% By:
%  + Javier Macías-Guarasa. 
%    Departamento de Electrónica
%    Universidad de Alcalá
%  + Roberto Barra-Chicote. 
%    Departamento de Ingeniería Electrónica
%    Universidad Politécnica de Madrid   
% 
% Based on original sources by Roberto Barra, Manuel Ocaña, Jesús Nuevo,
% Pedro Revenga, Fernando Herránz and Noelia Hernández. Thanks a lot to
% all of them, and to the many anonymous contributors found (thanks to
% google) that provided help in setting all this up.
%
% See also the additionalContributors.txt file to check the name of
% additional contributors to this work.
%
% If you think you can add pieces of relevant/useful examples,
% improvements, please contact us at (macias@depeca.uah.es)
%
% You can freely use this template and please contribute with
% comments or suggestions!!!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{List of Publications}
\label{cha:list_of_publications}

\begin{refsection}

The following publications (both journal papers and conference contributions) correspond to first author or main co-author. For a complete view of all publications derived from the thesis: \href{https://scholar.google.es/citations?user=OWwoG6EAAAAJ\&hl=es}{All publications} \footnote{https://scholar.google.es/citations?user=OWwoG6EAAAAJ\&hl=es}.

\section*{Journal Papers}

\begin{itemize}

\item \textbf{Gomez-Huelamo, C.}, Conde, M. V., Barea, R., Ocala, M, \& Bergasa, L. M. (2023). Efficient Baselines for Motion Prediction in Autonomous Driving. Transactions on Intelligent Transportation Systems. In submission.

\item \textbf{Gomez-Huelamo, C.}, Del Egido, J., Bergasa, L. M., Barea, R., Lopez-Guillen, E., Araluce, J., \& Antunes, M. (2022). 360º real-time and power-efficient 3D DAMOT for autonomous driving applications. Multimedia Tools and Applications, 81(19), 26915-26940

\item \textbf{Gómez-Huélamo, C.}, Del Egido, J., Bergasa, L. M., Barea, R., López-Guillén, E., Arango, F., ... \& López, J. (2021). Train here, drive there: Ros based end-to-end autonomous-driving pipeline validation in carla simulator using the nhtsa typology. Multimedia Tools and Applications, 1-28

\end{itemize}

\section*{Conference Contributions}

\begin{itemize}

\item \textbf{Gómez-Huélamo, C.}, Conde, M. V., Gutiérrez-Moreno R, Barea, R., Llamazares A., Antunes M., \& Bergasa, L. M. (2022, October). Efficient Context-Aware Graph Transformer for Vehicle Motion Predictio. In 2023 IEEE 26th International Conference on Intelligent Transportation Systems (ITSC). IEEE. In submission.

\item Gutiérrez-Moreno R., \textbf{Gómez-Huélamo, C.}, Barea. R, López-Guillén E., Arango F., Ortiz, M., \& Bergasa, L. M. (2023, October). Augmented Reinforcement Learning with Efficient Social-based Motion Prediction for Autonomous Decision-Making. In 2023 IEEE 26th International Conference on Intelligent Transportation Systems (ITSC). IEEE. In submission.

\item \textbf{Gómez-Huélamo, C.}, Conde, M, Barea, R. \& Bergasa, L. M. (2023, June). Improving Multi-Agent Motion Prediction with Heuristic Goals and Motion Refinement. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR) (pp. 5322-5331). IEEE

\item \textbf{Gómez-Huélamo, C.}, Conde, M. V., Ortiz, M., Montiel, S., Barea, R., \& Bergasa, L. M. (2022, October). Exploring Attention GAN for Vehicle Motion Prediction. In 2022 IEEE 25th International Conference on Intelligent Transportation Systems (ITSC) (pp. 4011-4016). IEEE

\item Diaz-Diaz, A., Ocaña, M., Llamazares, Á., \textbf{Gómez-Huélamo, C.}, Revenga, P., \& Bergasa, L. M. (2022, June). HD maps: Exploiting OpenDRIVE potential for Path Planning and Map Monitoring. In 2022 IEEE Intelligent Vehicles Symposium (IV) (pp. 1211-1217). IEEE.

\item \textbf{Gómez-Huélamo, C.}, Diaz-Diaz, A., Araluce, J., Ortiz, M. E., Gutiérrez, R., Arango, F., ... \& Bergasa, L. M. (2022, June). How to build and validate a safe and reliable Autonomous Driving stack? A ROS based software modular architecture baseline. In 2022 IEEE Intelligent Vehicles Symposium (IV) (pp. 1282-1289). IEEE

\item Del Egido, J., \textbf{Gómez-Huélamo, C.}, Bergasa, L. M., Barea, R., López-Guillén, E., Araluce, J., ... \& Antunes, M. (2020, November). 360 real-time 3d multi-object detection and tracking for autonomous vehicle navigation. In Advances in Physical Agents II: Proceedings of the 21st International Workshop of Physical Agents (WAF 2020), November 19-20, 2020, Alcalá de Henares, Madrid, Spain (pp. 241-255). Cham: Springer International Publishing.

\item \textbf{Gómez–Huélamo, C.}, Bergasa, L. M., Gutiérrez, R., Arango, J. F., \& Díaz, A. (2021, July). Smartmot: exploiting the fusion of hdmaps and multi-object tracking for real-time scene understanding in intelligent vehicles applications. In 2021 IEEE Intelligent Vehicles Symposium (IV) (pp. 710-715). IEEE.

\item Gutiérrez, R., Arango, J. F., \textbf{Gomez-Huélamo, C.}, Bergasa, L. M., Barea, R., \& Araluce, J. (2021, July). Validation Method of a Self-Driving Architecture for Unexpected Pedestrian Scenario in CARLA Simulator. In 2021 IEEE Intelligent Vehicles Symposium (IV) (pp. 1144-1149). IEEE.

\item \textbf{Gómez-Huélamo, C.}, Del Egido, J., Bergasa, L. M., Barea, R., López-Guillén, E., Arango, F., ... \& López, J. (2021). Train here, drive there: Simulating real-world use cases with fully-autonomous driving architecture in carla simulator. In Advances in Physical Agents II: Proceedings of the 21st International Workshop of Physical Agents (WAF 2020), November 19-20, 2020, Alcalá de Henares, Madrid, Spain (pp. 44-59). Springer International Publishing

\item \textbf{Gómez-Huélamo, C.}, Del Egido, J., Bergasa, L. M., Barea, R., Ocana, M., Arango, F., \& Gutiérrez-Moreno, R. (2020, September). Real-time bird’s eye view multi-object tracking system based on fast encoders for object detection. In 2020 IEEE 23rd International Conference on Intelligent Transportation Systems (ITSC) (pp. 1-6). IEEE.

\item \textbf{Gómez-Huelamo, C.}, Bergasa, L. M., Barea, R., López-Guillén, E., Arango, F., \& Sánchez, P. (2019, October). Simulating use cases for the UAH Autonomous Electric Car. In 2019 IEEE Intelligent Transportation Systems Conference (ITSC) (pp. 2305-2311). IEEE.

\end{itemize}

\end{refsection}

